Designing modular software: a case study in introductory statistics

### 2016-09-08 jcgs-paper-2016/paper.Rmd
Change title

---
title: "Designing modular software for reproducible analyses: a case study in introductory statistics"
author:
  - name: Eric Hare
    affiliation: Iowa State University
    department: Department of Statistics
  - name: Andee Kaplan
    affiliation: Iowa State University
    department: Department of Statistics
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: preamble.tex
    number_sections: yes
    template: jcgs_article.tex
fontsize: 12pt
abstract: |
   Modular programming is a development paradigm that emphasizes self-contained, flexible, and independent pieces of functionality. However, the rise of web-based software applications has presented new challenges for designing an extensible, modular software system. In this paper, we outline a framework for designing such a system, with a focus on reproducibility of the results. We present as a case study a Shiny-based web application called `intRo`, that allows the user to perform basic data analyses and statistical routines. Finally, we highlight some challenges we encountered when combining modular programming concepts with reactive programming as used by Shiny.
keywords: Interactivity, Programming Paradigms, Reactive Programming, Reproducibility, Statistical Software
bibliography: refs.bib
blind: false
---

>>>>

---
title: "Designing modular software: a case study in introductory statistics"
author:
  - name: Eric Hare
    affiliation: Iowa State University
    department: Department of Statistics
  - name: Andee Kaplan
    affiliation: Iowa State University
    department: Department of Statistics
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: preamble.tex
    number_sections: yes
    template: jcgs_article.tex
fontsize: 12pt
abstract: |
   Modular programming is a development paradigm that emphasizes self-contained, flexible, and independent pieces of functionality. However, the rise of web-based software applications has presented new challenges for designing an extensible, modular software system. In this paper, we outline a framework for designing such a system, with a focus on reproducibility of the results. We present as a case study a Shiny-based web application called `intRo`, that allows the user to perform basic data analyses and statistical routines. Finally, we highlight some challenges we encountered when combining modular programming concepts with reactive programming as used by Shiny.
keywords: Interactivity, Programming Paradigms, Reactive Programming, Reproducibility, Statistical Software
bibliography: refs.bib
blind: false
---
